%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.3 (30/3/2020)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
%\colorlet{awesome}{awesome-emerald} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
\definecolor{awesome}{HTML}{11610a} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Tim}{Baker}
\address{243-Gorge Rd E, Victoria, BC, Canada}
\mobile{+1 (250) 793-0920}

\email{tbakerx@gmail.com}
\homepage{www.timbakerdev.com}
\github{tbakerx}
\linkedin{timbakerx}
%\skype{skypeid}
%\stackoverflow{SOid}{SOname}
%\twitter{@twit}

\position{Full Stack Software Engineer{\enskip\cdotp\enskip}Security Specialist} % Your expertise/fields
\quote{``Security is always excessive, until it's not enough."} % A quote or statement

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{Lumen5}{196 W 6th Ave\\ Vancouver\\ BC} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Job Application for Javascript Engineer} % The title of the letter

\letteropening{To whom it may concern,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

\letterenclosure[Attached]{Resume} % Any enclosures with the letter

\makecvfooter{\today}{Tim Baker~~~·~~~Cover Letter}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed
  
%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}

%------------------------------------------------

\lettersection{About Me}

I am a Canadian/Irish full stack engineer and security specialist based out of Victoria, BC. I like to get my hands dirty in any and all areas of the product stack and I have a strong track record of taking projects from inception to deployment. I have played an integral role within my current tech team as an engineer, leader, and mentor. I am most comfortable in a Javascript-based stack with extensive experience with React, Typescript, Redux/Mobx, Node/Express, and Postgres; however, I am also familiar with a range of other languages and can adapt quickly to new environments.

%------------------------------------------------

\lettersection{Why Lumen5?}

I thrive in a startup environment where things move quickly, culture is key, and everyone shares a common passion. After researching a little bit, it seems this is exactly the type of workplace you have inspired and I could see myself fitting in well. I am looking for a change of pace where the company direction is clear, the product and goal is well established yet ripe for innovation and improvement, and I get to feel the satisfaction of my impact on the end product. As a developer, choice of tech stack is of vital importance as well, and it is really nice to see that the tech you've chosen matches my skill set perfectly.

%------------------------------------------------

\lettersection{Why Me?}

I have 2 years of experience as a full stack developer in a highly dynamic environment that has had me lead the development of multiple different projects from start to finish (details in resume) and I'm just as comfortable spinning up new API servers as creating performant React components. My recent experience has all been in a similar stack and would allow for a smooth transition for me to get up to speed quickly.

I am passionate about cybersecurity and am currently pursuing both the CompTia Security+ and EC-Council Certified Ethical Hacker certifications. This is an area that often doesn't get enough attention within development teams, and I would be happy to share my knowledge and offer my services in that area as well.



%------------------------------------------------